\textls[-0]{\thetitle}

### 2023-03-25 canonicitymodel.tex
edits

We note that, the interpretation of $\Wsup{i}{\wsig}{a}{b}$ is defined by $\CWsup$ (defined below). It will take three elements: $i$, a glued $(\Gsub{\denotesCC{a}}{\Glued{\gm}})$ and a glued $(\Gsub{\denotesCC{b}}{{\Glued{\gm^\uparrow}}})$.  As we mentioned earlier, $\Glued{\gm}$ is the equivalent form of $(\gm, \gm')$.

The interpretation for $\CaseSig{"A"}{"B"}{"R"}$ is also bullet-drowned. However, it should be read as the glued interpretation of $ \TyPi{A}{\TyPi {\TyPi{B}{\sub{R}{\SubstWeak{2}}}} {\sub{R}{\SubstWeak{2}}}} $, which is exactly from the debruinj indxed-version of the typing rule \ruleref{tyeq/casety}.

>>>>

The interpretation of $\Wsup{i}{\wsig}{a}{b}$ is defined via $\CWsup$, which is
in turn defined below. This construction takes three arguments as input: $i$, a glued
$(\Gsub{\denotesCC{a}}{\Glued{\gm}})$ and a glued
$(\Gsub{\denotesCC{b}}{{\Glued{\gm^\uparrow}}})$.  As mentioned earlier,
$\Glued{\gm}$ is an equivalent form of $(\gm, \gm')$.

%The interpretation for $\CaseSig{"A"}{"B"}{"R"}$ is also bullet-drowned. However, it should be read as the glued interpretation of $ \TyPi{A}{\TyPi {\TyPi{B}{\sub{R}{\SubstWeak{2}}}} {\sub{R}{\SubstWeak{2}}}} $, which is exactly from the debruinj indxed-version of the typing rule \ruleref{tyeq/casety}.
